\documentclass[12pt]{res}

\usepackage[colorlinks=true,linkcolor=urlblue,urlcolor=urlblue]{hyperref}
\usepackage[a4paper, left=0.75in, right=1.50in, top=0.75in]{geometry}
\usepackage[usenames, dvipsnames]{color}
\usepackage{enumitem}
\usepackage{fancyhdr}
\definecolor{urlblue}{RGB}{32, 32, 255}
\setlength{\textheight}{9.50in}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[R]{\thepage}

\begin{document}
    % Name:
    \name{Nick Miller\\[12pt]}

    % Address and contact info:
    \address{\bf
        ADDRESS\\
        :ADDRESS:\\
        :PHONE:
    }
    \address{\bf
        CONTACT\\
        {\href{mailto:nick@nmiller.info}{nick@nmiller.info}}\\
        {\href{https://linkedin.com/in/nickjm}{linkedin.com/in/nickjm}}\\
        {\href{https://github.com/jadefish}{github.com/jadefish}}
    }

    % Body:
    \begin{resume}
        \section{OVERVIEW}
            Software engineer with 9 years of experience developing robust,
            efficient solutions for distributed and co-located teams. Proven
            track record in delivering mission-critical features for high-impact
            projects utilized by millions globally. Expertise in cloud
            platforms, backend systems, and mobile applications.

        \section{EXPERIENCE}
            \vspace{-0.1in}

            % Evvnt:
            \begin{tabbing}
                \hspace{2.15in}\= \hspace{2.55in}\= \kill
                {\bf Senior Software Engineer}
                \>Evvnt Technologies Corp.
                \>Sep 2021 - present\\
                \>Traverse City, MI (remote)
            \end{tabbing}
            \vspace{-21pt}
            As a core part of the small team at Evvnt, I wear many hats and
            frequently design and ship fundamental features, fixes, and
            projects. Notably:
            \\
            \begin{itemize}[noitemsep]
                \item Led rewrite of mobile box office app, increasing
                      gate ticket sale revenue by over 30\% and enhancing user
                      experience and reliability.
                \item Implemented self-service features for event creators,
                      enabling automatic event and user acquisition without
                      sales intervention.
                \item Integrated Apple Pay and Google Pay for ticket purchases,
                      reducing checkout time and friction.
            \end{itemize}

            % RJG:
            \begin{tabbing}
                \hspace{2.15in}\= \hspace{2.55in}\= \kill
                {\bf Software Engineer}
                \>RJG, Inc.
                \>Jun 2020 - Sep 2021\\
                \>Traverse City, MI
            \end{tabbing}
            \vspace{-21pt}
            Developed features and fixes for Java- and AngularJS-based injection
            molding software deployed to air-gapped, on-site installations.
            \\
            \begin{itemize}[noitemsep]
                \item Worked closely with the product and hardware teams to
                      add support for Smartflow mold temperature regulators.
                \item Spearheaded effort to identify and more closely align core
                      product with key domain concepts.
                \item Dockerized the majority of the core product, enabling
                      faster iteration and local development.
            \end{itemize}

            % Geotix:
            \begin{tabbing}
                \hspace{2.15in}\= \hspace{2.55in}\= \kill
                {\bf Senior Software Engineer}
                \>Geotix
                \>Sep 2018 - Jun 2020\\
                \>Traverse City, MI
            \end{tabbing}
            \vspace{-21pt}
            Leveraged Ruby on Rails, PostgreSQL, Redis, AWS, and front-end
            technologies to deliver performant features and fixes to help scale
            the business to 50k+ monthly ticket sales.
            \\
            \begin{itemize}[noitemsep]
                \item Developed an automated onboarding system for terms of use
                      and privacy policies, eliminating manual processes.
                \item Implemented major enhancements, features, and fixes to our
                      open-source Ruby view layer DSL and front-end framework,
                      {\href{https://github.com/coprl/coprl}{COPRL}}.
                \item Overhauled the new-client onboarding experience, unifying
                      fragmented processes and significantly enhancing UX.
                \item Created an integration tool using AWS Lambda for GitHub,
                      Pivotal Tracker, and Jenkins.

            \end{itemize}

            % MacUpdate:
            \begin{tabbing}
                \hspace{2.15in}\= \hspace{2.35in}\= \kill
                {\bf Software Engineer}
                \>MacUpdate, LLC
                \>Feb 2015 - Sep 2018\\
                \>Traverse City, MI
            \end{tabbing}
            \vspace{-21pt}
            As a key member of the distributed team for the largest third-party
            Mac software distribution and sales platform, I designed and
            implemented data-driven solutions using PHP, AWS, and MySQL.
            \\
            \begin{itemize}[noitemsep]
                \item Designed and implemented a performance-critical RESTful
                      PHP API using Laravel for a next-generation desktop
                      product.
                \item Led the implementation of site-wide GDPR protections
                      within tight deadlines.
                \item Optimized critical SQL queries and code sections, reducing
                      technical debt and improving user and team experiences.
            \end{itemize}

        \section{SKILLS}
            \textbf{Languages}:
                \begin{itemize}[noitemsep]
                    \item Expert: Ruby, SQL, HTML, JS, CSS
                    \item Proficient: C\#/.NET, PHP, Go, and Lua
                    \item Competent: Python, shell scripting
                \end{itemize}
            \textbf{Tools}:
                git, vim, Docker, Visual Studio, Intellij IDEs,
                various text editors\\
            \textbf{Systems \& platforms}:
                AWS, Jenkins, macOS, Linux/UNIX, Windows, GitHub, Bitbucket,
                PostgreSQL, MySQL\\
            \textbf{Frameworks}:
                Ruby on Rails, Active Record, Zend, Laravel/Lumen, Doctrine\\
            \textbf{Miscellaneous}:
                Docker, CI/CD, unit testing, AJAX, RESTful APIs, OOP, TDD, DDD

        \section{EDUCATION}
            \textbf{B.S. Software Engineering, B.S. Computer Science}\\
            The University of Texas at Dallas, May 2015\\
            GPA: 3.6
    \end{resume}
\end{document}
